Influence of Connectivity on Dung Beetle Communities

### 2025-04-17 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
paragrapgh 1 and updating thesis bib.

Paragraph 1: Overall Topic & Why it is interesting and Important.     
  As human disturbances continue to expand into natural landscapes, intact habitats are becoming increasingly fragmented.Effects from isolation can vary, however as habitats are broken down community structures are significantly altered [@WOS:000419965700012]. This degradation of structure lends to loss in biodiversity on a global scale and interruptions in ecosystem processes and functions [@haddad_habitat_2015].

@@

>>>>

Paragraph 1: Overall Topic & Why it is interesting and Important.     
  As human disturbances continue to expand into natural landscapes, intact habitats are becoming increasingly fragmented. Effects from isolation can vary, however as habitats are broken down community structures are significantly altered [@WOS:000419965700012]. This degradation of structure lends to loss in biodiversity on a global scale and interruptions in ecosystem processes and functions [@haddad_habitat_2015].

Like many ecological processes, fragmentation is a complex and multifaceted phenomenon

@@

With experimental designs we are able to isolate factors might be contributing to ecological patterns and processes.
